Supplementary Materials

### 2020-05-05 analysis/analysis.Rmd
Running models

```{r eeg_import}
fl <- "rms_Occ_Odd.csv"

@@

#import
read_csv(paste("data/", fl, sep = ""), col_types = my_cols) %>%
  rename(wallpaper_group = "Row") %>%
  gather("subject", "rms", -wallpaper_group) %>%
  glimpse() -> d_eeg 
```

@@

read_csv("../Experiment/process_results/thresholds.csv", col_types = my_cols_threshold) %>%
  select(subject = "person", wallpaper_group = "group", threshold) %>%
  glimpse() -> d_dispthresh

@@

read_csv(paste("data/", fl, sep = ""), col_types = my_cols) %>%
  rename(wallpaper_group = "Row") %>%
  gather("subject", "rms", -wallpaper_group) -> d_eeg_occ_even

@@

read_csv(paste("data/", fl, sep = ""), col_types = my_cols) %>%
  rename(wallpaper_group = "Row") %>%
  gather("subject", "rms", -wallpaper_group) -> d_eeg_par_odd

@@

```{r eeg_prior_pred_check, cache=TRUE, echo=TRUE}
m_prior <- brm(data = d_eeg, 
  rms ~ wallpaper_group-1 + (1|subject),
  family = "lognormal", 
  prior = prior, 
  iter = n_iter ,
  sample_prior = 'only')
```

@@

>>>>

\tiny
```{r eeg_import}
fl <- "rms_Occ_Odd.csv"

@@

#import
read_csv(paste("data/", fl, sep = ""), col_types = my_cols) %>%
  rename(wg = "Row") %>%
  gather("subject", "rms", -wg) %>%
  glimpse() -> d_eeg 
```

@@

read_csv("../Experiment/process_results/thresholds.csv", col_types = my_cols_threshold) %>%
  select(subject = "person", wg = "group", threshold) %>%
  glimpse() -> d_dispthresh

@@

read_csv(paste("data/", fl, sep = ""), col_types = my_cols) %>%
  rename(wg = "Row") %>%
  gather("subject", "rms", -wg) -> d_eeg_occ_even

@@

read_csv(paste("data/", fl, sep = ""), col_types = my_cols) %>%
  rename(wg = "Row") %>%
  gather("subject", "rms", -wg) -> d_eeg_par_odd

@@

```{r eeg_prior_pred_check, cache=TRUE, echo=TRUE}
m_prior <- brm(data = d_eeg, 
  rms ~ wg-1 + (1|subject),
  family = "lognormal", 
  prior = prior, 
  iter = n_iter ,
  sample_prior = 'only')
```

@@

## Compute Posterior

### Fit Model to EEG Data

We will now fit the model to the data.

```{r eeg_fit_model, cache=TRUE}
m_eeg <- brm(data = d_eeg, 
             rms ~ wg-1 + (1|subject),
             family = "lognormal", 
             prior = prior, iter = n_iter,
             control = list(adapt_delta = 0.99))

summary(m_eeg)
```

We will now have at what the model predicts for the average participant (i.e, ignoring the random intercepts). If anybody else would like to suggest over sensible ways to summarise this model, do let me know! I've been trying to use some of the functions from the `tidybayes` package, and they don't (yet?) have much on random effects.

```{r, fig.cap ="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals."}

 # Extract samples from model
my_samples$eeg <- get_model_samples(m_eeg)

 # Tidy up a little
 my_models$eeg <- get_model_predictions(my_samples$eeg)

 # Plot
plot_model_output(
  my_models$eeg, d_eeg,
  "Model Fits for the odd-harmonic data from occipital electrodes",
  "orangered3", 
  "log(rms)")
```

### Fit Model to Display Duration Threshold Data

We will now fit the model to the data.

```{r threshold_fit_model, cache=TRUE, echo=FALSE}
m_threshold <- brm(data = d_dispthresh, 
                   threshold ~ wg-1 + (1|subject),
                   family = "lognormal", 
                   prior = prior, iter = n_iter,
                   control = list(adapt_delta = 0.99))

summary(m_threshold)
```

```{r, fig.cap ="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals."}
# Extract samples from model
my_samples$threshold <- get_model_samples(m_threshold)

# Tidy up a little
my_models$threshold <- get_model_predictions(my_samples$threshold)

# Plot
plot_model_output(my_models$threshold, d_dispthresh, 
                  "Model Fits: Display Duration Threshold", "orangered3", "threshold (ms)")
```
